\pkg{dataMaid}: your assistant for data cleaning in \proglang{R}

### 2017-01-03 latex/article_vol2.tex
Fixed typos and made script

\begin{Schunk}
\begin{Sinput}
> library(dataMaid)
> data(toyData)
> toydata
\end{Sinput}
\begin{Soutput}
   var1 var2  var3        var4 var5       var6
1   red    1     a -0.65959383    1 Irrelevant
2   red    1     a  0.08671649    2 Irrelevant
3   red    1     a -0.10951326    3 Irrelevant
4   red    2     a  0.08630221    4 Irrelevant
5   red    2     a -1.84311184    5 Irrelevant
6   red    6     b  0.92210680    6 Irrelevant
7   red    6     b  1.01921086    7 Irrelevant
8   red    6     b -0.92428326    8 Irrelevant
9   red  999     c -0.65340163    9 Irrelevant
10  red   NA     c  0.21133941   10 Irrelevant
11 blue    4     c  0.91783009   11 Irrelevant
12 blue   82     .  0.10313983   12 Irrelevant
13 blue   NA        0.16954218   13 Irrelevant
14 <NA>  NaN other  0.41967230   14 Irrelevant
15 <NA>    5 OTHER  0.77143836   15 Irrelevant
\end{Soutput}
\begin{Sinput}
> clean(toyData)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> missVar2 <- identifyMissing(toyData$var2)
> str(missVar2)
\end{Sinput}
\begin{Soutput}
List of 3
 $ problem      : logi TRUE
 $ message      : chr "The following suspected missing value codes enter as 
 		 regular values: \\\"999\\\", \\\"NaN\\\"."
 $ problemValues: num [1:2] 999 NaN
 - attr(*, "class")= chr "checkResult"
\end{Soutput}
\end{Schunk}
The most important thing to note here is that while the printed
message is made for easy reading, the actual values of the variable
causing the issue are still obtainable in the element
\R{problemValues}. If we for instance decide that the values \R{999}
and \R{NaN} in \R{var2} are in fact miscoded missing values, we can
easily replace them with \R{NA}s:
\begin{Schunk}
\begin{Sinput}
> toyData$var2[toyData$var2 %in% missVar2$problemValues] <- NA
> identifyMissing(toyData$var2}
\end{Sinput}
\begin{Soutput}
No problems found.
\end{Soutput}
\end{Schunk}
% $

@@

\begin{Schunk}
\begin{Sinput}
> clean(toyData, render = FALSE, openResult = FALSE}
> render("dataMaid_toyData.Rmd", quiet = FALSE)
\end{Sinput}
\end{Schunk}
This also deals with the fact that \pkg{dataMaid} can produce
\pkg{rmarkdown} files that supersedes the upper size limit of code editors, e.g.
RStudio, which currently has an editor file size limit of 5MB. %\hl{dette giver
%ingen mening uden en præcision? "upper size limit" af hvad? Se udkommenteret 
%kommentar.}
% of RStudio,
%which is currently \hl{find number} GBs (using RStudio version
%1.0.44). 
%\hl{Is this maybe too editor specific? On the other hand, a
%  lot of people do use RStudio...}.

>>>>

\begin{Schunk}
\begin{Sinput}
> library(dataMaid)
> data(toyData)
> toyData
\end{Sinput}
\begin{Soutput}
   var1 var2  var3        var4 var5       var6
1   red    1     a -0.65959383    1 Irrelevant
2   red    1     a  0.08671649    2 Irrelevant
3   red    1     a -0.10951326    3 Irrelevant
4   red    2     a  0.08630221    4 Irrelevant
5   red    2     a -1.84311184    5 Irrelevant
6   red    6     b  0.92210680    6 Irrelevant
7   red    6     b  1.01921086    7 Irrelevant
8   red    6     b -0.92428326    8 Irrelevant
9   red  999     c -0.65340163    9 Irrelevant
10  red   NA     c  0.21133941   10 Irrelevant
11 blue    4     c  0.91783009   11 Irrelevant
12 blue   82     .  0.10313983   12 Irrelevant
13 blue   NA        0.16954218   13 Irrelevant
14 <NA>  NaN other  0.41967230   14 Irrelevant
15 <NA>    5 OTHER  0.77143836   15 Irrelevant
\end{Soutput}
\begin{Sinput}
> clean(toyData)
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> missVar2 <- identifyMissing(toyData$var2)
> str(missVar2)
\end{Sinput}
\begin{Soutput}
List of 3
 $ problem      : logi TRUE
 $ message      : chr "The following suspected missing value codes enter as 
 		 regular values: \\\"999\\\", \\\"NaN\\\"."
 $ problemValues: num [1:2] 999 NaN
 - attr(*, "class")= chr "checkResult"
\end{Soutput}
\end{Schunk}
The most important thing to note here is that while the printed
message is made for easy reading, the actual values of the variable
causing the issue are still obtainable in the element
\R{problemValues}. If we for instance decide that the values \R{999}
and \R{NaN} in \R{var2} are in fact miscoded missing values, we can
easily replace them with \R{NA}s:
\begin{Schunk}
\begin{Sinput}
> toyData$var2[toyData$var2 %in% missVar2$problemValues] <- NA
> identifyMissing(toyData$var2)
\end{Sinput}
\begin{Soutput}
No problems found.
\end{Soutput}
\end{Schunk}
% $

@@

\begin{Schunk}
\begin{Sinput}
> clean(toyData, render = FALSE, openResult = FALSE)
> render("dataMaid_toyData.Rmd", quiet = FALSE)
\end{Sinput}
\end{Schunk}
This also deals with the fact that \pkg{dataMaid} can produce
\pkg{rmarkdown} files that supersedes the upper size limit of code editors, e.g.
RStudio, which currently has an editor file size limit of 5MB. %\hl{dette giver
%ingen mening uden en præcision? "upper size limit" af hvad? Se udkommenteret 
%kommentar.}
% of RStudio,
%which is currently \hl{find number} GBs (using RStudio version
%1.0.44). 
%\hl{Is this maybe too editor specific? On the other hand, a
%  lot of people do use RStudio...}.
